```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fixest)
```

```{r}
h1b_df <- read.csv("clean_data/h1b_FY2021_FY2024.csv")
edu_h1b_df <- h1b_df %>%
  filter(!is.na(has_grad_degree) & !is.na(naics_code) & !is.na(city) & !is.na(lottery_year))
```

## How much variance in whether an applicant has an advanced degree can be explained by industry, city, and lottery year? 

Dimmock, Huang, and Weisbenner (2021) circumvent the issue of missing degree level data by leveraging industry-city-year fixed effects. In particular, they find that, in an independent prevailing wage dataset, these fixed effects explain 73% of variation in whether an applicant has an advanced degree. I test whether the same is true in the present data for the subset of applicants who have degree level data (i.e. the lottery winners). 

```{r}
linear_explanatory_model <- feols(has_grad_degree ~ 1|naics_code^city^lottery_year, data = edu_h1b_df)
summary(linear_explanatory_model)
```

```{r}
logit_explanatory_model <- feglm(has_grad_degree ~ 1|naics_code^city^lottery_year, data = edu_h1b_df, family = "logit")
summary(logit_explanatory_model)
```